NURM: a tool to locate numerical differences in pipelines

### 2019-05-28 paper.tex
More comments and edits

\subsection{Tree analysis}

@@

Files written by multiple processes also lead 
to unknown labels. To address this issue for a file F 
written by processes in \textbf{P} = \{$P_{1}$, \ldots $P_{n}$\}, we 
(1) check that processes in \textbf{P} do not write concurrently to F, 
(2) we establish an order on \textbf{P} based on the creation timestamp 
of the processes, (3) we replace ever process $P_{i}$ in \textbf{P} by 
a wrapper that first calls $P_{i}$ and then backs up F to a read-only 
directory. Thus, multiple versions of F are saved and used in the 
analysis.

Furthermore, cycles may be present in the process tree in case a file 
was written by more than one process. We remove such cycles by removing 
file edges between processes A and B when A's process creation 
timestamp is posterior to B's or when A=B. Indeed, such edges cannot 
happen in practice unless A and B were running concurrently, which we 
assume is not the case (we also checked that on the workflow we 
tested).

we first capture temporary and overwritten files in condition 1
we set various 
breakpoints in the pipeline in condition 2 to check the output files 
produced by each process after running. We then label processes in 4 
categories. When processes that create differences are 
found, their written files in condition 2 are replaced (as explained 
later) and then re-label processes. This procedure (stop/resume) 
continues until the end of the pipeline execution when all processes 
are labeled correctly.

\subsubsection{Unknown process}

Another challenge is to label processes that read files that have 
differences and write files that also have differences. In such 
situations, it is not possible to determine from the pipeline results 
whether the process created differences, removed some differences, or 
was transparent. We label such processes \emph{unknown}.
To address this issue, we first set various breakpoints in the pipeline 
in condition 2. Breakpoints are set by replacing all the pipeline 
processes with a custom script. This custom script labels each process 
as \emph{transparent}, \emph{create differences}, \emph{remove 
differences} or \emph{unknown} immediately after running original executable. 
The replacement is done through the PATH variable, as before. Moreover, 
this custom script copies the results obtained from the same process in 
condition 1 to the pipeline output in condition 2 if it is invoked with 
the arguments of a process that created differences. 
We developed an incremental approach that consists of the following steps:

\begin{enumerate}
  \item Run the pipeline in conditions 2; after running each process 
  label it as \emph{transparent}, \emph{create differences} or
  \emph{remove differences}.

  \item If there is \emph{create differences} processes then: 
  copies the results produced by the same process in condition 1 to the 
  pipeline output in condition 2.

@@

This algorithm converges to a process tree without any 
\emph{unknown} process at the end of the pipeline execution.

>>>>

\subsection{Graph analysis}

@@

Files written by multiple processes also lead 
to undetermined labels. For a file F 
written by all processes in \textbf{P} = \{$P_{1}$, \ldots $P_{n}$\}, we 
(1) check that processes in \textbf{P} do not write concurrently to F, 
(2) we establish an order on \textbf{P} based on the creation timestamp 
of the processes, (3) we replace every process $P_{i}$ in \textbf{P} by 
a wrapper that first calls $P_{i}$ and then backs up F to a read-only 
directory \tristan{add example of wrapper}. Thus, multiple versions of F are saved and used in the 
analysis.

Furthermore, cycles may be present in the process graph in case a file 
was written by more than one process. We remove such cycles by removing 
file edges between processes A and B when A's process creation 
timestamp is posterior to B's or when A=B. Indeed, such edges cannot 
happen in practice unless A and B were running concurrently, which we 
assume is not the case (the tool checks for that).

we first capture temporary and overwritten files in condition 1
we set various 
breakpoints in the pipeline in condition 2 to check the output files 
produced by each process after running. We then label processes in 4 
categories. When processes that create differences are 
found, their written files in condition 2 are replaced (as explained 
later) and then re-label processes. This procedure (stop/resume) 
continues until the end of the pipeline execution when all processes 
are labeled correctly. \tristan{this looks completely out of place}

\tristan{Explain that condition 1 is re-executed after all these modifications are done?}

\subsubsection{Labelling undetermined processes}

Another challenge is to label undetermined processes that read files with 
differences and write files with differences too. In such 
situations, it is not possible to determine from the pipeline results 
whether the process created differences, removed some differences, or 
was transparent.
To address this issue, we set breakpoints in the pipeline 
in Condition 2. Breakpoints are set by replacing all the pipeline 
processes with a custom script. This custom script labels each process 
as \emph{transparent}, \emph{create differences}, \emph{remove 
differences} or \emph{undetermined} immediately after running the original executable. 
The replacement is done through the PATH variable, as before. Moreover, 
this custom script copies the results obtained from the same process in 
Condition 1 to the pipeline output in Condition 2 if it is invoked with 
the arguments of a process that created differences. 
We developed an incremental approach that consists of the following steps:

\tristan{Not sure that we should call that breakpoints now.}

\tristan{Why do you need to modify condition 2 now, couldn't this be done on codition 1 too?}

\begin{enumerate}
  \item Run the pipeline in Condition 2; after running each process 
  label it as \emph{transparent}, \emph{create differences} or
  \emph{remove differences}.

  \item If there is \emph{create differences} processes then: 
  copies the results produced by the same process in condition 1 to the 
  pipeline output in Condition 2.

@@

This algorithm converges to a process tree without any 
\emph{undetermined} process at the end of the pipeline execution.

\tristan{Now that you're doing this, do you still need subject clustering? It looks like this isn't
much longer than regular execution.}
